To log or not to log

### 2022-06-04 main.tex
latest update

Forecasts play an important role in decision-making in epidemiology and public health [Citations], as well as other areas as diverse as for example economics [Citations] or agriculture [Citations]. Epidemiological modelling was an important tool to inform public policy throughout the COVID-19 pandemic and scenario modelling, as well as forecasts of cases, hospitalisations and deaths from COVID-19 have received widespread attention. Beginning in 2020, forecasts from different research institutions have been systematically collected, aggregated and evaluated by COVID-19 Forecast hubs in the US [Citation], Germany and Poland, and Europe [Citation].

>>>>

Forecasts play an important role in decision-making in epidemiology and public health [Citations], as well as other areas as diverse as for example economics [Citations] or agriculture [Citations]. Epidemiological modelling has been an important tool to inform public policy throughout the COVID-19 pandemic and scenario modelling, as well as forecasts of cases, hospitalisations and deaths from COVID-19 have received widespread attention. Beginning in 2020, forecasts from different research institutions have been systematically collected, aggregated and evaluated by COVID-19 Forecast hubs in the US [Citation], Germany and Poland, and Europe [Citation].
